\textbf{\huge EHDA closed loop control system based on real time non-visual spray mode classification}\\ (Center, Bold, Times New Roman 14, maximum 15 words in english)

### 2023-01-19 Documentation/UFMG/Relatorio_3/Development/Development.tex

% \subsection*{3.1 Setup and Routine Algorithm Optimization}

>>>>

\subsection*{3.1 Pump Integration}

    The pump integration in the automation algorithm bring us a new controllable variable, the Flowrate. Now we can control the spraying mode with the
    two main variables that afect the system. 
    It will bring more complexity for the system since now we are dealing with multivariable control.
    Fortunatelly those two variables are uncuppled (* be certain of that first *) which means that actuating in one of them will not interfere in the other one.
    Controlling also the flowrate gives to this project a new dimension in the system giving us freedom to explore the flowrate properties.

    The pump integration was developed using also python language. As I could not find a good library for this pump I developed an quick and easy interface for sending the pump
    commands to be integrated with the main automation routine. The communication with the pump was made using the serial interface and the commands list were found in the pump user manual.

\subsection*{3.2 First mapping Experiments}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{images/map2Data.png}
        \caption{Mapping Experiment data}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{images/map1.png}
        \caption{First mapping trial}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{images/map2.png}
        \caption{Second mapping trial}
    \end{figure}

    It was noticed that the motor of the pump in certains speed generate a noise caused by the stepping from the stepper motor.
    This noise from the motor was being acquired by the current data and was interfering in the classification method.
    Because of that the firsts results of the map have a lot of undefined or incorrect classifications.
    This can be reduced inserting a bubble in the syringe to atenuate mechanical noises.

### 2023-01-19 Documentation/WT group/article1/main.tex

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		\textbf{Electrohydrodynamic Atomization (EHDA)} also known as Electrospray (ES), is a technology that uses a strong electric field (kV/cm) to manipulate liquid breakup into droplets. This technique allows the generation of droplets smaller than the nozzle diameter with a controlled droplet size, which means it can be used to produce uniformly sized particles in the micro/nanoscale range. This liquid spraying technique can generate different modes when both the liquid flow rate and the voltage vary with a narrow size dispersion. The most known mode is the cone-jet mode, because it can produce droplets in the micro and nanometric range with a narrow size dispersion.
		The article presents a novel closed-loop control system for electrohydraulic actuators (EHDA) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. The system utilizes current data from the experiment to classify the spray mode dynamics in real-time and adjust the EHDA parameters, such as pump flowrate and power supply voltage, to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The results of the system are discussed and its potential applications in industrial settings are highlighted.
		consists of objectives, methods, findings, and research contributions in 150 to 250 words which contains the main conclusions and provides important information and is accompanied by \textbf{5 keywords}. Furthermore, the determination of keywords needs to pay attention to important words contained in the title and abstract, separated by a semicolon. \textbf{The novelty} in this paper briefly explains why no one else has adequately researched the question. Then \textbf{the results} are made a list of the empirical findings and write the discussion in one or two sentences. \\ \\
		\let\thefootnote\relax\footnotetext{
			\small $^{*}$\textbf{Corresponding author.} \textit{
				\textit{E-mail address: \color{cyan}author4@email.com}}\\
			\color{black} Received: xx xxxxx 20xx,\quad
			Accepted: xx xxxxx 20xx and available online XX July 2022 \\
			\color{cyan} https://doi.org/10.1016/j.compeleceng.2021.107553

>>>>

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size. The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The potential applications of the system are discussed, including in industrial processes such as spray coating and inkjet printing. EHDA has been widely used in various fields such as agriculture, biomedical and energy, specifically in the production of micron- and nano-size droplets for better control and efficient in the process.

		\let\thefootnote\relax\footnotetext{
			\small $^{*}$\textbf{Corresponding author.} \textit{
				\textit{E-mail address: \color{cyan}author4@email.com}}\\
			\color{black} Received: xx xxxxx 20xx,\quad
			Accepted: xx xxxxx 20xx and available online XX July 2022 \\
			\color{cyan} https://doi.org/10.1016/j.compeleceng.2021.107553
